Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-02-05 ThesisJP/Background/background.tex
Started adding figures in background section.

General introduction to ultrasound, GPUs etc...

\section{General-purpose computing on graphics processing units}

@@

Add sentence about siemens and supersonic imagine scanners.

\section {Ultrasound imaging}

@@

@@

@@

>>>>

In this chapter the background information needed in order to understand the topics of this thesis and its papers is given. First, in Section \ref{sec:gpgpu} an introduction to general purpose programming on graphics processing units (\nom{GPGPU}{General purpose programming on graphics processing units}) is presented. Next, an introduction to ultrasound imaging is given in Section \ref{sec:ultrasound}.

\section{General-purpose computing on graphics processing units}\label{sec:gpgpu}

@@

Add sentence about siemens and supersonic imagine scanners. They use GPUs? What does this mean? FPGAs and ASICs.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{img/free_lunsh.png}
\caption{Illustration of several transitions currently taking place in the computer industry. \todo{Site Herb Sutter - Welcom to the jungle http://herbsutter.com/welcome-to-the-jungle/}}
\label{fig:jungle}
\end{figure}

\begin{figure}
\centering
\subfigure[Threads, blocks and grid]{
	\includegraphics[width=0.4\textwidth]{img/cuda_threads.png}
}
\subfigure[Kernel]{
	\includegraphics[width=0.5\textwidth]{img/kernel.pdf}
}
\caption{Depicts how GPU threads are grouped into blocks and arranged in a grid. One thread runs a copy of a kernel function, in this example an element-wise matrix square operation.}
\label{fig:gpu_grid}
\end{figure}

\section {Ultrasound imaging}\label{sec:ultrasound}
Ultrasound imaging encompasses technology which generates images based on sound whose frequencies we can not hear. For medical ultrasound imaging frequencies above 2 MHz are typically used.

@@

\begin{figure}
\centering
\subfigure{
	\includegraphics[width=0.47\textwidth]{img/Diagram_of_the_human_heart.png}
}
\subfigure{
	\includegraphics[width=0.47\textwidth]{img/HeartWall.png}
}
\caption{Overview of the human heart. Illustrations from wikipedia.org.}
\label{fig:human_heart}
\end{figure}

@@

\begin{figure}[t!]
\subfigure[Delay-and-sum]{
	\includegraphics[width=0.47\textwidth]{img/scenario_das_resp2.png}
}
\subfigure[Capon]{
	\includegraphics[width=0.47\textwidth]{img/scenario_mv_resp2.png}
}
\caption{Array beam pattern with uniform and Capon weights. An interfering source is located at 20 degrees.}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[Ray-casting]{
	\includegraphics[width=0.4\textwidth]{img/Volumeraycasting.png}
}
\subfigure[Opacity transfer function]{
	\includegraphics[width=0.5\textwidth]{img/otf.png}
}
\caption{.}
\label{fig:vr}
\end{figure}
